---
title: "Binomial Package"
author: "Stella Cui"
date: "2019/5/2"
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(binomial)
```
**Binomial Package**
  * Author Name: Stella Cui

## Overview

`"binomial"` is a minimal [R](http://www.r-project.org/) package that calculates the relative probability of the certain number of successes in the given total number of trials. 

* `bin_mean()` for the mean of your desired binomial distribution.
* `bin_variance` for the variance of your desired binomial distribution.
* `bin_mode` for the mode of your desired binomial distribution.
* `bin_skewness` for the skeweneww of your desired binomial distribution.
* `bin_kurtosis` for the mean of your desired binomial distribution.

## Motivation
This package has been developed to illustrate some of the usage of Binomial Package.

## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 
# install "cointoss" (without vignettes)
devtools::install_github("stellacui1011/binomial")
# install "cointoss" (with vignettes)
devtools::install_github("stellacui1011/binomial", build_vignettes = TRUE)
```

## Usage
* First, loading the package using library(Binomial)
* Second, choosing the function you want to test
* Third, choosing your input, such as the number of trails, that of successes, and probability
* Fourth, get the output from your inputs and functions
```{r}
#The followings are various examples of using my Binomial package
bin_choose(n=10,k=1)
bin_probability(1,10,0.1)
bin_cum <- bin_cumulative(5,0.1)
plot(bin_cum)
bin_mean(2,0.1)
bin_variance(2,0.1)
bin_mode(10,0.1)
bin_skewness(10,0.1)
```
**trials = n, successes = k, and probability = prob or p**