---
title: "Vignettes"
author: "Stella Cui"
date: "2019/5/2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(binomial)
library(ggplot2)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The 'html_vignette' output type provides a custom style sheet (and tweak some options) to ensure 

-Never use retina figures
-Has a smaller default figure size
-Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

##binomial

The package "binomial" is a minimal implementation for calculating the relative probability of number of successes in total trials by using the given number of trials, successes and probability.

###1). Choose inputs for binomial variables
You can choose inputs by using the function "bin_choose(n,k)", where n is the total number of trials and k is the number of successes in trials.
```{r}
bin_choose(n=10,k=2)
```
###2). Get the probability of the given inputs n, k, and prob
Get the probability with the given inputs (number of trials(n), successes(k), and probability(p))
You can get the probability by applying the function bin_probability(k,n,p) after choosing those three inputs.
```{r}
bin_probability(success=2,trials=5,prob =0.5)
```
###3).Get a dataframe with the given inputs (k, n, and prob)
After choosing the inputs, you can get a dataframe with a consecutive number of trials from 0 to n and their corresponding probability using the function bin_distribution(n,p). 
```{r}
distribution1 <- bin_distribution(trials=10, prob=0.2)
distribution1
```
###4). Plot the probability dataframe
Plot the histogram of the probability dataframe got through bin_distribution(n,p) using the function plot().
```{r}
plot(distribution1)
```
###5). Getting cumulative probabilities for all possible successes values
After choosing the inputs n, k, p, you will get a dataframe with a consequtive number of trails from 0 to nand their corresponding probability p and their commulative probability by the function bin_cumulative(n,p).
```{r}
bin_cum <- bin_cumulative(trials = 5,prob=0.2)
bin_cum
```
###6). Plot cumulative probabilities for all possible successes values
Plotting the probability and cumulative dataframe we got before using the function plot().
```{r}
plot(bin_cum)
```
###7). Create a binomial variable with your desired inputs (n and p)
You can create a "bin_var" with the function bin_variable(n,p).
```{r}
bin_var <- bin_variable(trials = 5, prob = 0.3)
bin_var
```
###8). Get a summary of your binomial variable
You can use the function summary() to get a summary of binomial variables.
```{r}
bin_sum <- summary(bin_var)
bin_sum
```
###9). Various measure of your binomial variable
To get more details of your binomial variables, you can use the following funcions.
```{r}
bin_mean #for the mean of your desired binomial distribution.
bin_variance #for the variance of your desired binomial distribution.
bin_mode #for the mode of your desired binomial distribution.
bin_skewness #for the skeweneww of your desired binomial distribution.
bin_kurtosis #for the mean of your desired binomial distribution.
```

